A Gaussian process model of human electrocorticographic data

### 2019-12-09 paper/main.tex
added new corrmat stability analysis

We used this general approach to
quantify the algorithm's performance across the full dataset.For each held-out electrode, from each held-out patient in turn, we
computed the average correlation (across recording sessions) between
the SuperEEG-reconstructed voltage traces and the observed voltage
traces from that electrode.  For this analysis we set $\bar{R}$ to be
the union of all electrode locations across all patients.  This
yielded a single correlation coefficient for each electrode location
in $\bar{R}$, reflecting how well the SuperEEG algorithm was able to
recover the recording at that location by incorporating data across
patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations
was centered well above zero (mean: 0.52; $t$-test comparing mean of
distribution of $z$-transformed average patient correlation coefficients
to 0: $t(66) = 25.08, p < 10^{-10}$), indicating that the SuperEEG algorithm
recovers held-out activity patterns substantially better than random
guessing.

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model learned from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from that single patient may be used to estimate held-out data from
the same patient.  This allows us to ask how much information about
the activity at a given electrode might be inferred through (a) volume
conductance or other sources of ``leakage'' from activity patterns
measured from the patient's other electrodes and (b) across-electrode
correlations learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: 0.32;
$t$-test comparing mean of distribution of $z$-transformed average
patient correlation coefficients to 0: $t(66) = 15.16, p < 10^{-10}$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(66) = 9.62, p < 10^{-10}$).  This
is an especially conservative test, given that the across-patient
SuperEEG reconstructions exclude (from the correlation matrix
estimates) all data from the patient whose data is being
reconstructed.  We repeated each of these analyses on a second
independent dataset and found similar results
(Fig.~\ref{fig:corrmap}B, D; within versus across reconstruction
accuracy: $t(23) = 6.93, p < 10^{-5}$). We also replicated this result
separately for each of the two experiments from Dataset 2
(Fig.~\perexpcorrmaps).  This overall finding, that reconstructions of
held-out data using correlation models learned from \textit{other}
patient's data yield higher reconstruction accuracy than correlation
models learned from the patient whose data is being reconstructed, has
two important implications.  First, it implies that distant electrodes
provide additional predictive power to the data reconstructions beyond
the information contained solely in nearby electrodes.  (This follows
from the fact that each patient's grid, strip, and depth electrodes
are implanted in a unique set of locations, so for any given electrode
the closest electrodes in the full dataset tend to come from the
same patient.)  Second, it implies that the spatial correlations
learned using the SuperEEG algorithm are, to some extent, similar
across people.

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 1 (Panel C) or Dataset 2
    (Panel D).  The dot colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location.}
  \label{fig:corrmap}
\end{figure}

The recordings we analyzed from Dataset 1 comprised data collected as
the patients performed a variety of (largely idiosyncratic) tasks
throughout each day's recording session.  That we observed reliable
reconstruction accuracy across patients suggests that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across tasks.  We tested this finding more directly using
Dataset 2.  In Dataset 2, the recordings were limited to times when
each patient was participating in each of two experiments (Experiment
1, a random-word list free recall task, and Experiment 2, a
categorized list free recall task).  We wondered whether a correlation
model learned from data from one experiment might yield good
predictions of data from the other experiment.  Further, we wondered
about the extent to which it might be beneficial or harmful to combine
data across tasks.

To test the task-specificity of the SuperEEG-derived correlation
models, we repeated the above within- and across-patient cross validation
procedures separately for Experiment 1 and Experiment 2 data from
Dataset 2.  We then compared the reconstruction accuracies for held-out
electrodes, for models trained within versus across the two
experiments, or combining across both experiments
(Fig.~\perexptaskrecon).  In every case we found that across-patient
models trained using data from all other patients out-performed
within-patient models trained on data only from the subject
contributing the given electrode ($t$s$(23) > 6.50, p$s$ < 10^{-5}$).  All
reconstruction accuracies also reliably exceeded chance performance
($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average reconstruction accuracy was
highest for the across-patient models limited to data from the same
experiment (mean accuracy: $0.68$); next-highest for the
models that combined data across both experiments (mean
accuracy: $0.61$); and lowest for models trained across tasks (mean
accuracy: $0.47$).  This result also held for each of the Dataset 2
experiments individually (Fig.~\perexptaskreconseparated).  Taken
together, these results indicate that there are reliable commonalities
in the spatial correlations of full-brain activity across tasks, but
that there are also reliable differences in these spatial correlations
across tasks.  Whereas reconstruction accuracy benefits from
incorporating data from other patients, reconstruction accuracy is
highest when constrained to within-task data, or data that includes a
variety of tasks (e.g., Dataset 1, or combining across the two Dataset
2 experiments).

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}C, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes in the dataset
that were contained within a 20 MNI unit radius sphere centered on
that voxel.  We defined the \textit{density} at that location as this
proportion.  Across Datasets 1 and 2, the electrode placement
densities were similar (correlation by voxel:
$r = 0.56, p < 10^{-10}$).  We wondered whether regions with good
covererage might be associated with better reconstruction accuracy
(e.g. Fig.~\ref{fig:corrmap}C, D indicate that many electrodes in the
MTL have relatively high reconstruction accuracy, and occipital
electrodes tend to have relatively low reconstruction accuracy).  To
test whether this held more generally across the entire brain, for
each dataset we computed the electrode placement density for each
electrode from each patient (using the proportion of \textit{other}
patients' electrodes within 20 MNI units of the given electrode).  We
then correlated these density values with the across-patient
reconstruction accuracies for each electrode.  We found no reliable
correlations between reconstruction accuracy and density for either
dataset (Dataset 1: $r = 0.09, p = 0.44$; Dataset 2:
$r = -0.30, p = 0.15$).  This indicates that the reconstruction
accuracies we observed are not driven solely by sampling density, but
rather may also reflect higher order properties of neural dynamics
such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and B).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each given
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are potentially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = 0.20, p < 10^{-10}$).  While the
correspondence between the two maps was imperfect, our finding that
there were some commonalities between the two maps lends support to
the notion that different brain areas are differently informative
about full-brain activity patterns.  We also examined the intersection
between the top 10\% most informative voxels across the two datasets
(white outlines in Fig.~\ref{fig:informap}A, B, Fig.~\intersectmap).
Supporting the notion that structures that are highly interconnected
with the rest of the brain might be especially good targets for
implantation, this intersecting set of voxels with the highest
information scores included major portions of the dorsal attention
network (e.g., inferior parietal lobule, precuneus, inferior temporal
gyrus, thalamus, and striatum) as well as some portions of the default
mode network (e.g., angular gyrus) that are highly interconnected with
a large proportion of the brain's gray matter~\citep[e.g., ][]{TomaVolk11}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between the
    top 10\% most informative voxels in each map (also see
    Fig.~\intersectmap).  \textbf{C. Correspondence in information
      scores by voxel across Datasets 1 and 2.}  Same format as
    Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

>>>>

We used this general approach to
quantify the algorithm's performance across the full dataset.For each held-out electrode, from each held-out patient in turn, we
computed the average correlation (across recording sessions) between
the SuperEEG-reconstructed voltage traces and the observed voltage
traces from that electrode.  For this analysis we set $\bar{R}$ to be
the union of all electrode locations across all patients.  This
yielded a single correlation coefficient for each electrode location
in $\bar{R}$, reflecting how well the SuperEEG algorithm was able to
recover the recording at that location by incorporating data across
patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations
was centered well above zero (mean: 0.51; $t$-test comparing mean of
distribution of $z$-transformed average patient correlation coefficients
to 0: $t(66) = 23.55, p < 10^{-10}$), indicating that the SuperEEG algorithm
recovers held-out activity patterns substantially better than random
guessing.

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model learned from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from that single patient may be used to estimate held-out data from
the same patient.  This allows us to ask how much information about
the activity at a given electrode might be inferred through (a) volume
conductance or other sources of ``leakage'' from activity patterns
measured from the patient's other electrodes and (b) across-electrode
correlations learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: 0.32;
$t$-test comparing mean of distribution of $z$-transformed average
patient correlation coefficients to 0: $t(66) = 15.16, p < 10^{-10}$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(66) = 9.17, p < 10^{-10}$).  This
is an especially conservative test, given that the across-patient
SuperEEG reconstructions exclude (from the correlation matrix
estimates) all data from the patient whose data is being
reconstructed.  We repeated each of these analyses on a second
independent dataset and found similar results
(Fig.~\ref{fig:corrmap}B, D; within versus across reconstruction
accuracy: $t(77) = 11.25, p < 10^{-10}$). We also replicated this result
separately for each of the two experiments from Dataset 2
(Fig.~\perexpcorrmaps).  This overall finding, that reconstructions of
held-out data using correlation models learned from \textit{other}
patient's data yield higher reconstruction accuracy than correlation
models learned from the patient whose data is being reconstructed, has
two important implications.  First, it implies that distant electrodes
provide additional predictive power to the data reconstructions beyond
the information contained solely in nearby electrodes.  (This follows
from the fact that each patient's grid, strip, and depth electrodes
are implanted in a unique set of locations, so for any given electrode
the closest electrodes in the full dataset tend to come from the
same patient.)  Second, it implies that the spatial correlations
learned using the SuperEEG algorithm are, to some extent, similar
across people.

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} The colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface.}
  \label{fig:corrmap}
\end{figure}

The recordings we analyzed from Dataset 1 comprised data collected as
the patients performed a variety of (largely idiosyncratic) tasks
throughout each day's recording session.  That we observed reliable
reconstruction accuracy across patients suggests that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across tasks.  We tested this finding more directly using
Dataset 2.  In Dataset 2, the recordings were limited to times when
each patient was participating in one of two experiments.  Experiment
1 is a random-word list free recall task; Experiment 2 is a
categorized list free recall task (24 patients particpated in both).  We wondered whether a correlation
model learned from data from one experiment might yield good
predictions of data from the other experiment.  Further, we wondered
about the extent to which it might be beneficial or harmful to combine
data across tasks.

To test the task-specificity of the SuperEEG-derived correlation
models, we restricted the dataset to the 24 patients that participated
in both experiments and repeated the above within- and across-patient cross validation
procedures separately for Experiment 1 and Experiment 2 data from
Dataset 2.  We then compared the reconstruction accuracies for held-out
electrodes, for models trained within versus across the two
experiments, or combining across both experiments
(Fig.~\perexptaskrecon).  In every case we found that across-patient
models trained using data from all other patients out-performed
within-patient models trained on data only from the subject
contributing the given electrode ($t$s$(23) > 6.50, p$s$ < 10^{-5}$).  All
reconstruction accuracies also reliably exceeded chance performance
($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average reconstruction accuracy was
highest for the across-patient models limited to data from the same
experiment (mean accuracy: $0.68$); next-highest for the
models that combined data across both experiments (mean
accuracy: $0.61$); and lowest for models trained across tasks (mean
accuracy: $0.47$).  This result also held for each of the Dataset 2
experiments individually (Fig.~\perexptaskreconseparated).  Taken
together, these results indicate that there are reliable commonalities
in the spatial correlations of full-brain activity across tasks, but
that there are also reliable differences in these spatial correlations
across tasks.  Whereas reconstruction accuracy benefits from
incorporating data from other patients, reconstruction accuracy is
highest when constrained to within-task data, or data that includes a
variety of tasks (e.g., Dataset 1, or combining across the two Dataset
2 experiments).

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}C, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes in the dataset
that were contained within a 20 MNI unit radius sphere centered on
that voxel.  We defined the \textit{density} at that location as this
proportion.  Across Datasets 1 and 2, the electrode placement
densities were similar (correlation by voxel:
$r = 0.6, p < 10^{-10}$).  We wondered whether regions with good
covererage might be associated with better reconstruction accuracy
(e.g. Fig.~\ref{fig:corrmap}C, D indicate that many electrodes in the
MTL have relatively high reconstruction accuracy, and occipital
electrodes tend to have relatively low reconstruction accuracy).  To
test whether this held more generally across the entire brain, for
each dataset we computed the electrode placement density for each
electrode from each patient (using the proportion of \textit{other}
patients' electrodes within 20 MNI units of the given electrode).  We
then correlated these density values with the across-patient
reconstruction accuracies for each electrode.  We found a negative
correlation between reconstruction accuracy and density for Dataset 1,
but was unreliable for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$; Dataset 2:
$r = -0.30, p = 0.15$).  This indicates that the reconstruction
accuracies we observed are not driven by sampling density, but
rather may also reflect higher order properties of neural dynamics
such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and B).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each given
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are potentially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = 0.18, p < 10^{-10}$).  While the
correspondence between the two maps was imperfect, our finding that
there were some commonalities between the two maps lends support to
the notion that different brain areas are differently informative
about full-brain activity patterns.  We also examined the intersection
between the top 10\% most informative voxels across the two datasets
(gray areas in Fig.~\ref{fig:informap}C).
Supporting the notion that structures that are highly interconnected
with the rest of the brain might be especially good targets for
implantation, this intersecting set of voxels with the highest
information scores included major portions of the dorsal attention
network (e.g., inferior parietal lobule, precuneus, inferior temporal
gyrus, thalamus, and striatum) as well as some portions of the default
mode network (e.g., angular gyrus) that are highly interconnected with
a large proportion of the brain's gray matter~\citep[e.g., ][]{TomaVolk11}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between the
    top 10\% most informative voxels in each map (also see
    Fig.~\intersectmap).  \textbf{C. Intersection.}  
    Gray areas indicate the intersections between the
    top 10\% most informative voxels in each map.  \textbf{D. Correspondence in information
      scores by voxel across Datasets 1 and 2.}  Same format as
    Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

We also wondered what frequency properties contributed to the
reconstruction accuracy.  For this analysis, we INSTERT TUDORS
DESCRIPTION FOR FREQ ANALYSIS.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/frequency}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets for each frequency band.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 1.}  The across-patient
    distribution (left jitter barplot) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (right
    jitter barplot in lighter color)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B.~Statistical summary of across-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
    map, warmer colors (positive t-values) indicate that the
    distribution of
    reconstruction accuracy for the frequency band in a given row
    yielded was greater than the frequency band in the given
    column. Cooler colors (negative t-values) indicate that the
    frequency band in the given row yielded lower reconstruction
    accuracy than the frequency band in the given column. The lower
    triangles of each map denote the corresponding p-values for the
    t-tests. The diagonal entries display the relative average
    reconstruction accuracy given to each frequency band. \textbf{C.~Statistical summary ofwithin-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.}
    This panel displays the within-patient statistical summary,
    in the same format as Panel B.  \textbf{D.~Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 2.}  This panel displays
    reconstruction accuracy distributions for each frequency band for
    Dataset 2 in
    the same format as Panel A. \textbf{E.~Statistical summary of
      across-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.} This is the same format as Panel
    B for Dataset 2. \textbf{F.~Statistical summary of
      within-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.}This is the same format as Panel
    C for Dataset 2.}
  \label{fig: frequency}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/networks}
  \caption{\textbf{Electrode sampling density by location.}
    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
    voxel is colored by the proportion of total electrodes in the
    dataset that are
    located within a 20~MNI unit radius sphere centered on the given
    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
      2.}  This panel displays the sampling density map for Dataset 2,
    in the same format as Panel A.  \textbf{C.~Correspondence in
      sampling density by voxel across Datasets 1 and 2.}  The
    two-dimensional histogram displays the by-voxel densities in the
    two Datasets, and the one-dimensional histograms display the
    proportions of voxels in each dataset with the given density
    value.  The correlation reported in the panel is across voxels in
    the 4~mm$^3$ MNI brain.}
  \label{fig: networks}
\end{figure}
